{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-06-21 bmvc_review.tex
Update Figures

\textbf{Performance on UAV123 Dataset} We used the precision and
success rate metrics to compare the performance of the proposed
algorithm with those of the state-of-the-art high speed tracking
algorithms. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF \cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF \cite{henriques2015high},
MOSSE \cite{bolme2010visual,henriques2015high}, and STC \cite{zhang2014fast} and ones in relatively
lower-speed ($\geq$50): SAMF \cite{li2014scale}, DSST
\cite{danelljan2014accurate}, Struck \cite{hare2012efficient}, MUSTER
\cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}. Figure \ref{fig:UAV123_DATASET} shows the
results on the UAV123 dataset. {\it E}nKCF outperformed most of the
high-speed tracking methods by $3\%$-$15\%$ at 20 pixels
precision. Three algorithms, SAMF, DSST, and Struck did about 5\%
better than ours in accuracy, but 10-20 times slower. For the scale
adaptation, {\it E}nKCF did second best in terms of AUC for the
success rate plot. It outperformed other tracking methods in
high-speed by about $20\%$-$25\%$ in AUC. In addition, it performed
even better than those algorithms that are slow, but a slightly better
in precision. For example, for AUC, {\it E}nKCF outperformed Struck
and DSST by $5\%$ and $10\%$ while running at more than $10$ and $30$
times faster.
\begin{figure}[!h]
\raggedright
\begin{tabular}{ccc}
\tiny\textbf{UAV123}\hspace{.45\linewidth}\textbf{OTB100}\\
\bmvaHangBox{\includegraphics[width=2.80cm]{./figures/pr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_otb100.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_otb100.eps}}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with other trackers on the UAV123 and OTB100 datasets.}
\label{fig:UAV123_DATASET}
\end{figure}

@@

\begin{figure}[!h]
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_uav123_10fps.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_uav123_10fps.eps}}\\
\end{tabular}
\caption{Comparison of a modified {\it E}nKCF's performance with those
  of the state-of-the-art tracking algorithms on the UAV123$\_$10fps
  dataset where the original UAV123 data was temporally downsampled.}
\label{fig:UAV123_10fpsDATASET}
\end{figure}

>>>>

\textbf{Performance on UAV123 Dataset} We used the precision and
success rate metrics to compare the performance of the proposed
algorithm with those of the state-of-the-art high speed tracking
algorithms. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF \cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF \cite{henriques2015high},
MOSSE \cite{bolme2010visual,henriques2015high}, and STC \cite{zhang2014fast} and ones in relatively
lower-speed ($\geq$50): SAMF \cite{li2014scale}, DSST
\cite{danelljan2014accurate}, Struck \cite{hare2012efficient}, MUSTER
\cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}. Figure \ref{fig:UAV123_DATASET} shows the
results on the UAV123 dataset. {\it E}nKCF outperformed most of the
high-speed tracking methods by $3\%$-$15\%$ at 20 pixels
precision. Three algorithms, SAMF, DSST, and Struck did about 5\%
better than ours in accuracy, but 10-20 times slower. For the scale
adaptation, {\it E}nKCF did second best in terms of AUC for the
success rate plot. It outperformed other tracking methods in
high-speed by about $20\%$-$25\%$ in AUC. In addition, it performed
even better than those algorithms that are slow, but a slightly better
in precision. For example, for AUC, {\it E}nKCF outperformed Struck
and DSST by $5\%$ and $10\%$ while running at more than $10$ and $30$
times faster.
\begin{figure}[!h]
\raggedright
\begin{tabular}{ccc}
\tiny\quad\textbf{UAV123}\hspace{.45\linewidth}\textbf{OTB100}\\
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.25cm]{./figures/sr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_otb100.eps}}
\bmvaHangBox{\includegraphics[width=3.25cm]{./figures/sr_otb100.eps}}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with other trackers on the UAV123 and OTB100 datasets.}
\label{fig:UAV123_DATASET}
\end{figure}

@@

\begin{figure}[!h]
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_uav123_10fps.eps}}
\bmvaHangBox{\includegraphics[width=3.25cm]{./figures/sr_uav123_10fps.eps}}\\
\end{tabular}
\caption{Comparison of a modified {\it E}nKCF's performance with those
  of the state-of-the-art tracking algorithms on the UAV123$\_$10fps
  dataset where the original UAV123 data was temporally downsampled.}
\label{fig:UAV123_10fpsDATASET}
\end{figure}
